Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-04-05 paper/07-experiment.tex
paper updates

CCVPN is implemented as a networking layer service running on the gateways of private networks (see Fig.\ref{fig:ccvpn}).
Our implementation uses the CCNx software stack~\cite{CCNxGithub} and the cryptographic library Sodium~\cite{sodiumGithub}. These are both publicly available and are written in C.
The interest encapsulation routine (Alg.\ref{alg:interestEncap}) is implemented using

>>>>

CCVPN is implemented as a network layer service running on the gateways of private networks that compose the VPN (see Fig.\ref{fig:ccvpn}).
Our implementation uses the CCNx software stack~\cite{CCNxGithub} and the cryptographic library Sodium~\cite{sodiumGithub}. These are both publicly available and written in C.
For the PKE version of CCVPN, interest encapsulation and decapsulation routines (Alg.~\ref{alg:interestEncap}, and . Alg.~\ref{alg:interestDecap}) are implemented using \todo{check alg} as public key
encryption (and decryption) algorithm. \todo{check alg} is used to encrypt-then-MAC the content reponses (Alg.~\ref{alg:contentEnc}, and Alg.~\ref{alg:contentDec}). Recall that the symmetric keys used by
\todo{check alg} are generated and sent together with the encapsulated interest in Alg.~\ref{alg:interestEncap}.
In the symmetric key version of the design, \todo{check alg} was used to encrypt-then-MAC both, interests and contents.
